Speed and strength of an epidemic intervention

### 2020-01-24 doc/speedstrength.tex
Time for lab meeting

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/test_and_treat.pdf}
\caption{
\textbf{Understanding test-and-treat intervention using strength- and speed-based decomposition.}
\swp{We should just say exponentially. I see where you're coming from but the super-exponentiality seems negligible. Plotting on a log scale shows that it's approximately linear.}
(A) The effectiveness of test-and-treat intervention is assumed to increase super-exponentially at first, and then saturate. The dashed line shows the corresponding effective strength of the intervention (from \eqref{strengthMean}) assuming 23\% early transmission.
(B) Increase in the estimated amount of early transmission decreases the estimated strength of an epidemic as well as the estimated strength of test-and-treat intervention.
(C) The hazard rate correesponding to the strength curve in (A). 
The dashed line shows the corresponding effective speed of the intervention (from \eqref{speedMean}) assuming 23\% early transmission.
(D) The estimated amount of early transmission does not affect the observed speed of an epidemic but affects the estimated speed of intervention.
The black and red circles indicate the baseline scenario.
Test-and-treat intervention is modeled phenomenologically: $\tsub{L}{test}(\tau) = \exp\left(\int_0^\tau \tsub{h}{test}(\sigma) d\sigma \right)$ and $\tsub{h}{test}(\tau) = \tsub{h}{max} (1 - \exp(- K f(\tau)))$, where $f(\tau)$ is a gamma probability density function with a mean of $1$ year and a shape parameter of 2, $K = 4/\max(f(\tau))$, and $\tsub{h}{max} = 2\,\mathrm{year}^{-1}$.
}
\figlab{test}
\end{figure}

>>>>

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/test_and_treat.pdf}
\caption{
\textbf{Understanding test-and-treat intervention using strength- and speed-based decomposition.}
(A) The strength of the test-and-treat intervention (calculated from the assumed hazard, (C)). The dashed line shows the corresponding effective strength of the intervention (from \eqref{strengthMean}) assuming 23\% early transmission.
(B) Increase in the estimated amount of early transmission decreases the estimated strength of an epidemic as well as the estimated strength of test-and-treat intervention.
(C) The assumed hazard for the test-and-treat intervention. 
The dashed line shows the corresponding effective speed of the intervention (from \eqref{speedMean}) assuming 23\% early transmission.
(D) The estimated amount of early transmission has little effect on the effective speed of intervention, and none on the speed of the epidemic estimated from incidence data.
Circles indicate the baseline scenario.
Test-and-treat intervention is modeled phenomenologically: $\tsub{L}{test}(\tau) = \exp\left(\int_0^\tau \tsub{h}{test}(\sigma) d\sigma \right)$ and $\tsub{h}{test}(\tau) = \tsub{h}{max} (1 - \exp(- K f(\tau)))$, where $f(\tau)$ is a gamma probability density function with a mean of $1$ year and a shape parameter of 2, $K = 4/\max(f(\tau))$, and $\tsub{h}{max} = 2\,\mathrm{year}^{-1}$.
}
\figlab{test}
\end{figure}

\jd{I'm horrified that you would suggest saying ``exponentially'' in a non-technical sense in a scientific paper. Should we think about showing one or three generation intervals in panels a and c (intrinsic and backward respectively) to help people think about averaging?}
